### 2021-08-12 paper/paper.tex
Somewhat simplify statement

Many scientists implementing numerical methods often have no formal training
in software development. Julia and its ecosystem support these
researchers by making it easy to set up unit and regression tests, since a
testing framework is included in the standard library and default package
generation setups prepare the file structure accordingly. This allows test-driven
development and continuous integration (CI), which makes code restructuring
and optimization straightforward.

>>>>

Many scientists implementing numerical methods often have no formal training
in software development. Julia and its ecosystem support these
researchers by making it easy to set up unit and regression tests, since a
testing framework is included in the standard library. This facilitates test-driven
development and continuous integration (CI), which makes code restructuring
and optimization straightforward.
